% ================================================
% STRT 1.0 - Main Book Preface
% ================================================

\documentclass[12pt,a4paper]{book}
\usepackage{strt-packages}

\begin{document}

\frontmatter

\title{This Is the Dream}
\subtitle{Stafford's Transtemporal Resonance Theory (STRT 1.0)}
\author{Brent Stafford}
\date{May 2026}

\maketitle

\chapter*{Preface}

For over fifty years I have lived with a mystery that science said should not exist.

I have had dreams that came true \textemdash not in the vague, symbolic way of ordinary dreams, but with precise, verifiable detail. A chalkboard lesson I had never seen before. A conversation in a parking lot that matched word for word. A knife returned to me by a stranger who had never met me. A heart attack prevented because I lingered at a stop sign, recognizing the scene from a dream two weeks earlier.

These were not coincidences. They were not hallucinations. They were exact matches between what I experienced in sleep and what later unfolded in waking life.

For decades I kept this private. I told almost no one. Only after I began to understand the physics did I start to speak.

This book is the result.

It presents a new theory \textemdash Stafford's Transtemporal Resonance Theory (STRT 1.0) \textemdash that explains how consciousness can reach across time, and why the universe itself appears to be built on the same mechanism.

STRT is not speculation. It is a zero-parameter geometric framework derived from first principles. It unifies consciousness, quantum mechanics, gravity, and cosmology under a single compactification: $\mathbb{CP}^4 \times T^2$ with integer fluxes $F_3 = 6$, $F_5 = 12$. From this single object emerge the retrocausal weighting $\lambda = \phi^{-2} \approx 0.382$, the master resonance equation, the origin of qualia, the cosmological constant, low-power warp propulsion, and the arrow of time.

The theory makes dozens of falsifiable predictions, many of which are already being tested in laboratories around the world as of 2026.

This is not a book about belief. It is a book about physics.

If you are a physicist, I ask only that you evaluate the mathematics and the predictions with an open mind. If you are a lay reader, I ask you to consider the possibility that the universe is far more interconnected \textemdash and far more conscious \textemdash than we have been taught.

Either way, welcome.

This is the dream.

\vspace{1cm}
\hfill Brent Stafford\\
\hfill May 2026

\end{document}